\section{\textbf{Projects}}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Ufund Website} $|$ \emph{Angular, Java, Spring Boot, REST APIs, Docker}}{}
          \resumeItemListStart
            \resumeItem{Built a full-stack web application using Angular and Spring Boot with RESTful APIs in a team of four, following Agile/Scrum practices.}
            \resumeItem{Designed backend services using \textbf{object-oriented principles} with \textbf{90\%+} unit test coverage to ensure reliability and maintainability.}
            \resumeItem{Implemented \textbf{role-based access control}, \textbf{notifications}, and \textbf{search/filter functionality} to support secure and flexible user interactions.}
          \resumeItemListEnd
    \vspace{-5pt}
      \resumeProjectHeading
          {\textbf{Rapid Automation} $|$ \emph{Python (Pandas, scikit-learn), SQL}}{}
          \resumeItemListStart
            \resumeItem{Built an \textbf{end-to-end Python pipeline} to ingest, clean, and process outage data using Pandas.}
            \resumeItem{Trained and tuned an \textbf{SVC classification model} with \textbf{90\%+} accuracy to distinguish engineering vs. non-engineering outage events.}
            \resumeItem{Automated processing of \textbf{5,000+} outage records, improving operational efficiency.}
            \resumeItemListEnd
    \vspace{-5pt}
      \resumeProjectHeading
      {\textbf{Transformer Failure Classifier} $|$ \emph{Python (Pandas, scikit-learn, LightGBM), SQL}}{}  
        \resumeItemListStart
            \resumeItem{Built a \textbf{Python-based pipeline} to automatically parse \textbf{1,000+} PDF reports and convert unstructured transformer data into structured tabular datasets.}
            \resumeItem{Extracted data from \textbf{SQL} databases and parsed PDF reports with Python (Pandas), aggregating and cleaning the combined dataset for reliable model training.}
            \resumeItem{Developed a stacked ensemble classification model using \textbf{scikit-learn} and \textbf{LightGBM} to classify transformer failures using features derived from gas and oil sample data.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd